Reducing Power Consumption in Huffman Coding

### 2015-02-20 Switche Paper 1st approache/elsarticle-template-num.tex
good

\begin{tabular}{c  c c  c c  c c}
\hline
 & Huffman Algorithm & P \\\hline
\\\hline
Genome 1& 18.16 & 10.05 & 44.65 \\\hline
Genome 2& 24.66 &  15.63 & 36.61 \\\hline
Genome 3&18.46 &  10.66&  42.25\\\hline
Genome 4&25.18&16.26& 35.42\\\hline
Genome 5& 19.24& 16.08 & \\\hline
Genome 6& &\\\hline
Genome 7& &\\\hline
Genome 8& & \\\hline
Genome 9& &\\\hline
Genome 10& & \\\hline
Genome 11& & \\\hline
Genome 12& &\\\hline
Genome 13& &\\\hline
Genome 14& & \\\hline
Genome 15& & \\\hline
Genome 16&& \\\hline
Genome 17& & \\\hline
Genome 18& & \\\hline

>>>>

\begin{tabular}{c  c c  c c  c c}
\hline
 & Huffman Algorithm & P \\\hline
\\\hline
Genome 1& 18.16 & 10.05 & 44.65 \\\hline
Genome 2& 24.66 &  15.63 & 36.61 \\\hline
Genome 3&18.46 &  10.66&  42.25\\\hline
Genome 4&25.18&16.26& 35.42\\\hline
Genome 5& 19.24& 16.08 &16.42 \\\hline
Genome 6& 19.61&14.96&23.71\\\hline
Genome 7& 22.40 &13.21&41.02\\\hline
Genome 8&23.87 & \\\hline
Genome 9& &\\\hline
Genome 10& & \\\hline
Genome 11& & \\\hline
Genome 12& &\\\hline
Genome 13& &\\\hline
Genome 14& & \\\hline
Genome 15& & \\\hline
Genome 16&& \\\hline
Genome 17& & \\\hline
Genome 18& & \\\hline
